---
title: "CLT"
author: "Briana Barba"
date: '2022-06-08'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
Originalmean<-mean(my1000)
OriginalSD<-sd(my1000)
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 
The mean on the original data is `r Originalmean` and standard deviation is `r OriginalSD`.

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
Sample2mean<-mean(x.avg)
Sample2SD<-sd(x.avg)
```

The plot is not unimodal. There are also three peaks for a sample size of two. The two peaks on opposite ends are the same size but the one in the middle is bigger than the two side ones. The average mean is `r Sample2mean` and standard deviation is `r Sample2SD`.

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
Sample4mean<-mean(x.avg)
Sample4sd<-sd(x.avg)
```

The mean for sample 4 is `r Sample4mean` and standard deviation for sample 4 is `r Sample4sd`. There are 5 peaks in sample size 4 with them being 4 people not liking her to 1 out of 4, then to 2 out of 4 liking her, 3 out of 4 liking her and then ends with 4 out of 4 liking her. With the highest peak being at 2 out of 4 people liking her.

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
Sample9mean<-mean(x.avg)
Sample9sd<-sd(x.avg)
```


```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
Sample16mean<-mean(x.avg)
Sample16sd<-sd(x.avg)
```

```{r}
numb = 25
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 25")
Sample25mean<-mean(x.avg)
Sample25sd<-sd(x.avg)
```

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
Sample36mean<-mean(x.avg)
Sample36sd<-sd(x.avg)
```

Sample 36 mean is `r Sample36mean` and sample 36 standard deviation is `r Sample36sd`. 